%-------------------------------------------
% Resume: MASTER VERSION (All Projects + Full Activities)
%-------------------------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Ahmed Fathy} & Email: \href{mailto:ahmedfathi20044002@gmail.com}{ahmedfathi20044002@gmail.com}\\
  \textit{Software Engineer} & Mobile: +20 155 285 1443 \\
  \href{https://www.linkedin.com/in/ahmedfathy-x1}{LinkedIn} $|$ \href{https://github.com/ahmedfathy0-0}{Github} $|$ \href{https://www.mrfathi.tech/}{Portfolio} & Giza, Egypt \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cairo University, Faculty of Engineering}{Giza, Egypt}
      {B.Sc. in Computer Engineering;  GPA: 3.6}{2023 -- 2027}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Al Nada Scientific Office}{Cairo, Egypt}
      {IT Specialist}{June 2022 -- 2024}
      \resumeItemListStart
        \resumeItem{Database Application Development}
          {Designed and upgraded a database application from VBA/MS SQL to React, Express.js, and PostgreSQL, improving scalability and data access.}
        \resumeItem{Technical Maintenance}
          {Provided hands-on maintenance for electronic devices and collaborated with the team to support IT systems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------STUDENT ACTIVITIES-----------------
\section{Student Activities}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IEEE}{Cairo, Egypt}
      {UI/UX Designer - Frontend Team Leader}{Oct 2025 - Present}
      \resumeItemListStart
        \resumeItem{UI Design}
          {Designed intuitive and visually appealing user interfaces for internal platforms and event management tools.}
      \resumeItemListEnd

    \resumeSubheading
      {Technical Center for Career Development (TCCD)}{Cairo, Egypt}
      {Frontend Developer}{June 2025 - Present}
      \resumeItemListStart
        \resumeItem{HR System}
          {Developed an HR system to help HR members monitor events, track attendees, and manage participation.}
        \resumeItem{Web Maintenance}
          {Contributed to the development and maintenance of the official TCCD website.}
      \resumeItemListEnd

    \resumeSubheading
      {Physics Helping District (PhD)}{Cairo, Egypt}
      {Team Leader}{June 2022 - 2024}
      \resumeItemListStart
        \resumeItem{Mentorship}
          {Led a student initiative supporting peers in physics and electronics through tutoring, workshops, and practical demonstrations to improve academic performance.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS (ALL)-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Hankers (X-Clone)}
      {Large-scale social platform using React, TypeScript, Docker, and Microservices. Implemented CI/CD and complex state management.}
    \resumeSubItem{NexaMart}
      {Full-stack e-commerce bookstore using Next.js, Laravel 11, and MySQL with Sanctum authentication.}
    \resumeSubItem{Image Colorization \& Restoration}
      {AI pipeline for restoring historical photos using Python, FastAPI, OpenCV, and Deep Learning (Inpainting).}
    \resumeSubItem{Company Manager App}
      {ERP system for inventory and sales using React, Express.js, Prisma, and PostgreSQL.}
    \resumeSubItem{Tactic (AI \& Robotics)}
      {Game suite integrating AI (YOLOv5/OpenCV) and hardware control (ESP32) via WebSockets.}
    \resumeSubItem{Tayseer-Web}
      {Corporate website built with Next.js and TypeScript, utilizing SSR for SEO.}
    \resumeSubItem{Path Planning Study}
      {Implemented and analyzed A*, Dijkstra’s, and RRT algorithms in C++.}
    \resumeSubItem{Interactive Orrery}
      {3D solar system visualizer using React.js and Three.js.}
    \resumeSubItem{Alien Invasion}
      {C++ simulation game modeling combat scenarios using OOP and custom data structures.}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
 \resumeSubHeadingListStart
    \item{\textbf{Languages}{: JavaScript, TypeScript, PHP, Python, C++, SQL}}
    \item{\textbf{Frontend}{: React.js, Next.js, Redux, Tailwind CSS, Material-UI, Three.js}}
    \item{\textbf{Backend}{: Node.js, Express.js, Laravel, FastAPI, REST APIs}}
    \item{\textbf{Data \& AI}{: PostgreSQL, MySQL, MongoDB, OpenCV, YOLO, NumPy}}
    \item{\textbf{DevOps \& Tools}{: Docker, Git, GitHub, Linux}}
 \resumeSubHeadingListEnd

\end{document}