%-------------------------------------------
% Projects & Activities Database
%-------------------------------------------

% --- STUDENT ACTIVITIES ---
\newcommand{\resumeStudentActivities}{
    \resumeActivitySubheading
      {IEEE}{Cairo}{UI/UX Designer - Frontend Team Leader}{Oct 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Portfolio Platform Development}
          {Engineered comprehensive web platform featuring workshop and event management systems with admin dashboard for content creation, role-based access control enabling instructors to upload course materials and students to register for workshops and events.}
      \resumeItemListEnd
    \vspace{4pt}

    \resumeActivitySubheading
      {Technical Center for Career Development (TCCD)}{Cairo}{Frontend Developer}{June 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Portfolio Platform Development}
          {Developed comprehensive platform with event pages, admin dashboard for event creation, role-based access for instructors and students, location management, event galleries, and statistical analysis pages.}
        \resumeItem{HR Management \& Judging System}
          {Built HR system managing team attendance with custom form builder and reviewer functionality similar to Google Forms, alongside event judging system for evaluating and assessing teams applying to events.}
      \resumeItemListEnd
    \vspace{4pt}

    \resumeActivitySubheading
      {Physics Helping District (PhD)}{Cairo}{Team Leader}{June 2022 -- 2024}
      \resumeItemListStart
        \resumeItem{Mentorship}
          {Led peer tutoring initiative in electronics, achieving measurable academic improvement.}
      \resumeItemListEnd
}

\newcommand{\resumeStudentActivitiesSiemens}{
    \resumeActivitySubheading
      {IEEE}{Cairo}{UI/UX Designer - Frontend Team Leader}{Oct 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Leadership}
          {Architected intuitive user interfaces and optimized user journey protocols for internal platforms.}
      \resumeItemListEnd
    \vspace{4pt}

    \resumeActivitySubheading
      {Technical Center for Career Development (TCCD)}{Cairo}{Frontend Developer}{June 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Development}
          {Engineered HR dashboard for event tracking and spearheaded optimization of the official TCCD web.}
      \resumeItemListEnd
    \vspace{4pt}

    \resumeActivitySubheading
      {NASA Space Apps Challenge}{Cairo}{Participant -- Project: "Orrery"}{Oct 2024}
      \resumeItemListStart
        \resumeItem{Orrery App}
          {Developed an interactive orrery app visualizing near-Earth objects using React and Three.js.}
      \resumeItemListEnd
    \vspace{4pt}

    \resumeActivitySubheading
      {Physics Helping District (PhD)}{Cairo}{Team Leader}{June 2022 -- 2024}
      \resumeItemListStart
        \resumeItem{Mentorship}
          {Led peer tutoring initiative in electronics, achieving measurable academic improvement.}
      \resumeItemListEnd
}

% --- HARDWARE & EMBEDDED PROJECTS ---

\newcommand{\resumeProjectProcessor}{
    \resumeProjectSubheading
      {5-Stage Pipelined Processor (RISC)}{https://github.com/Exo1i/5-Stage-Pipelined-Processor.git}{VHDL, QuestaSim, Computer Architecture}{2025}
      \resumeItemListStart
        \resumeItem{Core Architecture}
          {Engineered a \textbf{32-bit 5-stage pipelined processor} in VHDL, supporting a custom ISA of over 25 instructions.}
        \resumeItem{Hazard Resolution}
          {Optimized throughput by implementing Hazard Detection and Data Forwarding units to resolve control and data dependencies.}
        \resumeItem{Verification}
          {Validated functional correctness through rigorous simulation and testbench environments in \textbf{QuestaSim}.}
      \resumeItemListEnd
}

\newcommand{\resumeProjectCNN}{
    \resumeProjectSubheading
      {CNN Convolution Accelerator}{https://github.com/AhmedSobhy01/convolution-accelerator.git}{Verilog, OpenLane2, ASIC Design}{2025}
      \resumeItemListStart
        \resumeItem{Architecture}
          {Designed a synthesizable \textbf{2D convolution accelerator} using \textbf{Systolic Arrays} and fully pipelined dataflow to maximize MAC throughput.}
        \resumeItem{Memory Hierarchy}
          {Implemented DMA-based loading and dual-port SRAM buffering to support up to \textbf{16x16 kernel} execution.}
        \resumeItem{Physical Design}
          {Executed RTL-to-GDSII synthesis using \textbf{OpenLane2}, validating physical feasibility and achieving timing closure.}
      \resumeItemListEnd
}

\newcommand{\resumeProjectAES}{
    \resumeProjectSubheading
      {AES Encryption/Decryption Engine}{https://github.com/ahmedfathy0-0/AES.git}{Verilog, FPGA, Cryptograph}{2023}
      \resumeItemListStart
        \resumeItem{Core Logic}
          {Synthesized robust AES cryptographic core in Verilog HDL supporting \textbf{128-bit, 192-bit, and 256-bit} key standards.}
        \resumeItem{Datapath}
          {Engineered hardware-optimized modules for SubBytes, ShiftRows, MixColumns, and AddRoundKey transformations.}
        \resumeItem{Validation}
          {Verified cryptographic correctness against standard NIST test vectors using rigorous debug tracing.}
      \resumeItemListEnd
}

\newcommand{\resumeProjectTactic}{
    \resumeProjectSubheading
      {Tactic (Robotics \& AI)}{https://github.com/roboSobia}{Embedded Systems}{2024}
      \resumeItemListStart
        \resumeItem{System Integration}
          {Developed browser-controlled robotics suite integrating AI computer vision with low-latency hardware control.}
        \resumeItem{Firmware}
          {Programmed ESP32 microcontrollers to handle WebSocket communication for real-time motor control and telemetry.}
        \resumeItem{Backend Processing}
          {Deployed YOLOv5 and OpenCV on host server to process visual feedback and automate robotic decision-making.}
      \resumeItemListEnd
}

\newcommand{\resumeProjectTacticIBM}{
    \resumeProjectSubheading
      {Tactic (Robotics \& AI)}{https://github.com/roboSobia}{Real-Time Systems, WebSockets, Embedded}{2024}
      \resumeItemListStart
        \resumeItem{Real-Time Messaging System}
          {Engineered a low-latency \textbf{WebSocket} communication layer to integrate a web dashboard with embedded hardware.}
        \resumeItem{Reliability}
          {Ensured reliable message delivery and system synchronization between the browser interface and the robotic unit.}
      \resumeItemListEnd
}

% --- SOFTWARE & WEB PROJECTS ---

\newcommand{\resumeProjectHankers}{
    \resumeProjectSubheading
      {Hankers (Social Platform)}{https://github.com/SWEProject25}{Full-Stack Engineering}{2025}
      \resumeItemListStart
        \resumeItem{Architecture}
          {Built scalable social platform using Microservices principles, React.js, and TypeScript.}
        \resumeItem{Frontend}
          {Implemented responsive UI design and asynchronous API integration via AJAX.}
        \resumeItem{DevOps}
          {Established CI/CD pipelines and containerized services using Docker for consistent deployment.}
      \resumeItemListEnd
}

\newcommand{\resumeProjectHankersIBM}{
    \resumeProjectSubheading
      {Hankers (Social Platform)}{https://github.com/SWEProject25}{Microservices, TypeScript, Docker, CI/CD}{2025}
      \resumeItemListStart
        \resumeItem{Scalable Microservices Architecture}
          {Designed a distributed system using \textbf{Microservices} and \textbf{TypeScript} to decouple services and ensure scalability.}
        \resumeItem{DevOps Automation}
          {Implemented \textbf{CI/CD pipelines} and \textbf{Docker} to automate testing and reliable delivery of services.}
      \resumeItemListEnd
}

\newcommand{\resumeProjectNexaMart}{
    \resumeProjectSubheading
      {NexaMart}{https://github.com/ahmedfathy0-0/NexaMart.git}{E-commerce Solution, Full-Stack}{2025}
      \resumeItemListStart
        \resumeItem{Stack}
          {Next.js (TypeScript), Redux Toolkit, Laravel 11, and MySQL.}
        \resumeItem{Functionality}
          {Implemented secure authentication (Sanctum), shopping cart logic, real-time order processing, and administrative analytics dashboard.}
      \resumeItemListEnd
}

\newcommand{\resumeProjectTayseer}{
    \resumeProjectSubheading
      {Tayseer-Web}{https://github.com/ahmedfathy0-0/Tayseer-web.git}{Corporate Web Solution, Next.js}{2024}
      \resumeItemListStart
        \resumeItem{Deployment}
          {Deployed corporate website utilizing Next.js framework and TypeScript.}
        \resumeItem{Performance}
          {Maximized performance via Server-Side Rendering (SSR) and strict static typing for reliability.}
      \resumeItemListEnd
}

\newcommand{\resumeProjectCompanyManager}{
    \resumeProjectSubheading
      {Company Manager App -- Al Nada Scientific Office}{https://github.com/Al-Nada-Company-Manager-App}{ERP System, React \& PostgreSQL}{2024}
      \resumeItemListStart
        \resumeItem{Tech Stack}
          {React.js, Redux, Express.js, Prisma, PostgreSQL, Electron for desktop deployment.}
        \resumeItem{Business Solution}
          {Developed ERP application for Al Nada Scientific Office managing customers, suppliers, inventory, and sales records.}
        \resumeItem{Deployment}
          {Packaged application with Electron for local server deployment, enabling offline usage.}
      \resumeItemListEnd
}

\newcommand{\resumeProjectBlog}{
    \resumeProjectSubheading
      {Blog Web Application}{https://github.com/ahmedfathy0-0/Pharoh-s-StarCode}{Content Management System, Node.js}{2024}
      \resumeItemListStart
        \resumeItem{Core Features}
          {Architected content platform with CRUD capabilities, rich-text editing (Quill), and secure image handling (Multer).}
      \resumeItemListEnd
}

\newcommand{\resumeProjectOrrery}{
    \resumeProjectSubheading
      {Interactive Orrery -- NASA Space Apps Hackathon}{https://github.com/ahmedfathy0-0/Pharoh-s-StarCode}{3D Space Simulation, React.js}{Oct 2024}
      \resumeItemListStart
        \resumeItem{Hackathon Project}
          {Developed during NASA Space Apps Challenge 2024, simulating orbital mechanics and near-Earth object trajectories using React.js and Three.js.}
      \resumeItemListEnd
}

% --- AI & ALGORITHMS ---

\newcommand{\resumeProjectImageColorization}{
    \resumeProjectSubheading
      {Image Restoration Pipeline}{https://github.com/ahmedfathy0-0/Image-Colorization-of-Historical-Photos}{Deep Learning \& Computer Vision, Python}{2024}
      \resumeItemListStart
        \resumeItem{Pipeline}
          {Constructed end-to-end restoration pipeline: Denoising, Deblurring, and Inpainting.}
        \resumeItem{Algorithms}
          {Applied Telea (FMM) inpainting and deep learning models to restore damaged historical photographs.}
      \resumeItemListEnd
}

\newcommand{\resumeProjectPathPlanning}{
    \resumeProjectSubheading
      {Path Planning Analysis}{https://github.com/ahmedfathy0-0/Path-Planing-Analysis}{Algorithm Benchmarking, C++}{2024}
      \resumeItemListStart
        \resumeItem{Performance}
          {Benchmarked pathfinding algorithms (A*, Dijkstra, RRT) analyzing computational complexity and execution time.}
      \resumeItemListEnd
}

% --- GAMES & SIMULATIONS ---

\newcommand{\resumeProjectBrickBreakers}{
    \resumeProjectSubheading
      {x86 Brick Breakers Arcade}{https://github.com/ahmedfathy0-0/Brick-Breakers-Game-Assembly-8086.git}{Assembly (x86), MASM, Low-Level Programming}{2024}
      \resumeItemListStart
        \resumeItem{Game Logic}
          {Developed a real-time, multiplayer arcade game using x86 Assembly and the MASM assembler.}
        \resumeItem{System Control}
          {Directly manipulated video memory for low-latency graphics rendering and managed hardware interrupts to handle real-time I/O.}
      \resumeItemListEnd
}

\newcommand{\resumeProjectAlienInvasion}{
    \resumeProjectSubheading
      {Alien Invasion}{https://github.com/ahmedfathy0-0/alien-invasion}{Combat Simulation, C++}{2023}
      \resumeItemListStart
        \resumeItem{Simulation}
          {Modeled combat scenarios using custom data structures to simulate fleet mechanics and collision detection.}
      \resumeItemListEnd
}

\newcommand{\resumeProjectPaint}{
    \resumeProjectSubheading
      {Paint For Kids}{https://github.com/ahmedfathy0-0/paint-app}{C++, OOP, Data Structures}{2023}
      \resumeItemListStart
        \resumeItem{Application}
          {Built desktop drawing application with shape tools, color fills, and interactive game modes.}
        \resumeItem{Design}
          {Applied OOP principles using polymorphism for extensible shape classes and Stack-based Undo/Redo system.}
      \resumeItemListEnd
}

%-------------------------------------------
% EDUCATION
%-------------------------------------------
\newcommand{\resumeEducation}{
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cairo University, Faculty of Engineering}{Giza, Egypt}
      {B.Sc. in Computer Engineering;  GPA: 3.6}{2022}
  \resumeSubHeadingListEnd
}

%-------------------------------------------
% EXPERIENCE (Modular by Role)
%-------------------------------------------

% For Hardware/Embedded Resume
\newcommand{\resumeExperienceHardware}{
  \resumeSubHeadingListStart
    \resumeActivitySubheading
      {Al Nada Scientific Office}{Cairo, Egypt}{Technical Support Trainee}{June 2022 -- 2024}
      \resumeItemListStart
        \resumeItem{Diagnostics \& Maintenance}
          {Troubleshot workstations and network equipment; performed firmware updates and preventive maintenance.}
        \resumeItem{Documentation}
          {Created systematic troubleshooting documentation to streamline hardware issue resolution.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
}

% For Hardware/Embedded/QA Resume
\newcommand{\resumeExperienceHardwareQA}{
  \resumeSubHeadingListStart
    \resumeActivitySubheading
      {Al Nada Scientific Office}{Giza, Egypt}{Technical Support Trainee}{June 2022 -- 2024}
      \resumeItemListStart
        \resumeItem{Root Cause Analysis}
          {Investigated and isolated hardware faults using systematic debugging, performing firmware updates and maintenance.}
        \resumeItem{Documentation}
          {Created automated troubleshooting workflows to streamline issue resolution.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
}

% For Software Resume
\newcommand{\resumeExperienceSoftware}{
  \resumeSubHeadingListStart
    \resumeActivitySubheading
      {Al Nada Scientific Office}{Cairo, Egypt}{Software Developer (Part-time)}{June 2022 -- 2024}
      \resumeItemListStart
        \resumeItem{Full-Stack Development}
          {Designed and built a custom ERP application using React.js, Express.js, and PostgreSQL to replace legacy spreadsheet-based workflows.}
        \resumeItem{Web Development}
          {Developed and enhanced company's official website using Next.js, optimized SEO for Google search rankings, and integrated ecommerce features for online product sales.}
        \resumeItem{Desktop Deployment}
          {Packaged the ERP application with Electron for local server deployment, enabling reliable offline operation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
}

% For Web Resume
\newcommand{\resumeExperienceWeb}{
  \resumeSubHeadingListStart
    \resumeActivitySubheading
      {Al Nada Scientific Office}{Cairo, Egypt}{Web Developer (Freelance)}{June 2022 -- 2024}
      \resumeItemListStart
        \resumeItem{Full-Stack Development}
          {Built custom ERP web application using React.js and PostgreSQL to replace legacy spreadsheet-based business processes.}
        \resumeItem{Frontend Engineering}
          {Designed responsive user interface with Redux state management and RESTful API integration.}
        \resumeItem{Deployment}
          {Configured Electron-based desktop deployment for local server usage.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
}

% For AI Resume
\newcommand{\resumeExperienceAI}{
  \resumeSubHeadingListStart
    \resumeActivitySubheading
      {Al Nada Scientific Office}{Cairo, Egypt}{Software Developer (Freelance)}{June 2022 -- 2024}
      \resumeItemListStart
        \resumeItem{Database Design}
          {Designed PostgreSQL database schema to structure customer, supplier, and inventory data for ERP application.}
        \resumeItem{Data Analysis}
          {Implemented reporting features to analyze sales trends and inventory status.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
}

%-------------------------------------------
% SKILLS (Modular by Focus)
%-------------------------------------------

% Hardware Skills
\newcommand{\resumeSkillsHardware}{
 \resumeSubHeadingListStart
    \item{\textbf{Digital Design \& Verification}{: Verilog HDL, VHDL, RTL Design, RISC-V ISA, MIPS Architecture, Pipeline Design, RTL-to-GDSII Flow, OpenLane2, DRC/LVS Verification, Static Timing Analysis, FSM Design}}
    \item{\textbf{Development Tools \& Platforms}{: ModelSim, QuestaSim, Intel Quartus Prime, GTKWave, ESP32, AVR/Arduino}}
    \item{\textbf{Programming Languages}{: C/C++ (Advanced), Python, x86 Assembly, MIPS Assembly}}
 \resumeSubHeadingListEnd
}

% Software Skills
\newcommand{\resumeSkillsSoftware}{
 \resumeSubHeadingListStart
    \item{\textbf{Programming Languages}{: C++ Programming, Python, JavaScript, TypeScript, SQL, PHP, Java, Assembly Language}}
    \item{\textbf{Core Computing Concepts}{: Data Structures, Algorithms, Object-Oriented Programming, Design Patterns, Operating Systems, System Architecture}}
    \item{\textbf{Systems Programming}{: Unix/Linux Development, Multithreading, Memory Management, Network Socket Programming}}
    \item{\textbf{Backend Development \& DevOps}{: Node.js Runtime, Express Framework, Laravel, RESTful APIs, Docker Containers, Git Version Control, CI/CD Pipelines}}
 \resumeSubHeadingListEnd
}

% Web Skills
\newcommand{\resumeSkillsWeb}{
 \resumeSubHeadingListStart
    \item{\textbf{Frontend Development}{: React.js Framework, Next.js, TypeScript, Redux State Management, Tailwind CSS, Material-UI Components, Three.js Graphics}}
    \item{\textbf{Backend \& Database Systems}{: Node.js Runtime, Express.js Framework, Laravel PHP, RESTful APIs, GraphQL, PostgreSQL, MySQL, MongoDB, Prisma ORM}}
    \item{\textbf{DevOps \& Development Tools}{: Docker Containers, Git Version Control, CI/CD Automation, Linux Administration, API Testing, Cloud Deployment}}
 \resumeSubHeadingListEnd
}

% Web Skills V2 (IBM Tailored)
\newcommand{\resumeSkillsWebIBM}{
 \resumeSubHeadingListStart
    \item{\textbf{Core Concepts}{: OOP, SOLID Principles, Design Patterns (Factory, Strategy, Singleton), Microservices Architecture, Clean Code}}
    \item{\textbf{Integration \& Backend}{: RESTful APIs, GraphQL, WebSockets (Messaging), JSON/XML Data Mapping}}
    \item{\textbf{DevOps \& Tools}{: CI/CD Pipelines, Docker, Git, Linux (Fedora)}}
    \item{\textbf{Languages \& DBs}{: TypeScript, Python, SQL (PostgreSQL/MySQL), Node.js}}
 \resumeSubHeadingListEnd
}

% AI Skills
\newcommand{\resumeSkillsAI}{
 \resumeSubHeadingListStart
    \item{\textbf{AI \& Machine Learning}{: Deep Learning, Computer Vision, CNNs, YOLO, Image Processing, Inpainting}}
    \item{\textbf{Data Science Libraries}{: NumPy, Pandas, SciPy, Matplotlib, Scikit-learn, OpenCV, Pillow}}
    \item{\textbf{Frameworks}{: PyTorch, TensorFlow, Keras}}
    \item{\textbf{Languages \& Tools}{: Python (Advanced), C++, SQL, Git/GitHub, Jupyter Notebooks}}
    \item{\textbf{Deployment}{: FastAPI, Flask, Docker, React.js (Frontend Integration)}}
 \resumeSubHeadingListEnd
}

% Siemens Skills
\newcommand{\resumeSkillsSiemens}{
 \resumeSubHeadingListStart
    \item{\textbf{Languages}{: Python (Advanced), Bash/Shell Scripting, C++, JavaScript/TypeScript, Verilog/VHDL}}
    \item{\textbf{Automation \& DevOps}{: Linux (Fedora/RedHat), Docker, CI/CD Pipelines, Git, Make/CMake}}
    \item{\textbf{Web \& Frameworks}{: React.js, Node.js, REST APIs}}
    \item{\textbf{Domain Knowledge}{: VLSI Design Flow, ASIC Verification, DRC/LVS Concepts, Static Timing Analysis}}
 \resumeSubHeadingListEnd
}

% Master Resume Skills (Broad Overview)
\newcommand{\resumeSkillsMaster}{
 \resumeSubHeadingListStart
    \item{\textbf{Programming Languages}{: TypeScript, JavaScript, Python, C++, PHP, SQL, VHDL, Verilog}}
    \item{\textbf{Frontend Engineering}{: React.js, Next.js, Redux Toolkit, Tailwind CSS, Material-UI, Three.js}}
    \item{\textbf{Backend \& Database}{: Node.js, Express.js, Laravel, FastAPI, PostgreSQL, MySQL, MongoDB, Prisma ORM}}
    \item{\textbf{AI \& Computer Vision}{: OpenCV, YOLOv5, NumPy, Pandas, Scikit-learn, PyTorch}}
    \item{\textbf{DevOps \& Tools}{: Docker, Git/GitHub, CI/CD Pipelines, Linux (Bash), Postman, Agile/Scrum}}
 \resumeSubHeadingListEnd
}
